Automated Verification of Stand-alone Solar Photovoltaic Systems

### 2019-04-06 Tex/elsevier/trindade_ren_and_sust_rev1.tex
new text

\begin{abstract}
With declining costs and increasing performance, the deployment of renewable energy systems is growing faster. In 2017, for the first time, the number of people without access to electricity dipped below 1 billion, but trends on energy access likewise fall short of global goals. Particular attention is given to stand-alone solar photovoltaic systems in rural areas or where grid extension is unfeasible. Tools to evaluate electrification projects are available, but they are based on simulations that do not cover all aspects of the design space. Automated verification using model checking has proven to be an effective technique to any kind of program verification. This paper marks the first application of software model checking to formally verify the design of a stand-alone solar photovoltaic system including solar panel, charge controller, battery, inverter, and electric load. Case studies, from real photovoltaic systems deployed in five different sites, ranging from 700W to 1,200W, were used to evaluate this proposed approach and to compare that with specialized simulation tools. Different verification tools were evaluated as well. Data from practical applications show the effectiveness of our approach, where specific conditions that lead to failures in a photovoltaic solar system are only detailed by the automated verification method.
\end{abstract}

@@

\section{Introduction}
Lack of access to clean and affordable energy is considered a core dimension of poverty~\cite{Hussein2012}. Progress has been made worldwide; in particular, the number of people without electricity access fell below 1 billion threshold for the first time in 2017~\cite{IEAweo2018}. The share of people without access to electricity from Africa is 58\%, while 19\% of the share comes from developing Asia, and 31\% from Latin America~\cite{IEAweo2018}. Numbers from Brazil show the aim to electrify 270 isolated places and 2.7 million of people until 2023~\cite{EPE2018}. Furthermore, there is a close relationship between the lack of energy and the low HDI (Human Development Index) of those localities.

@@

Formal methods based on model checking offer a great potential to obtain a more effective and faster verification in the design process~\cite{ClarkeHV18}.  
%with behavior that is, in principle, well determined. 
Any kind of system can be specified as computer programs using mathematical logic, which constitutes the intended (correct) behavior; then, one can try to give a formal proof or otherwise establish that the program meets its specification. %User or project requirements can be added during the creation of the formal model to be verified. %, as defined by \cite{Trindade}. 
%
%This area of research is referred as formal methods. % as defined in \cite{Clarkeetal}.
% Their aim is to establish system correctness with mathematical rigor. 
%In the recent decades, research in formal methods has led to the development of very promising verification techniques.
% that facilitate the early detection of bugs in order to ensure the correctness of the system. 
%
%Model-based verification techniques are based on models that describe the possible system behavior in a mathematically precise and unambiguous manner. 
%Thus, such problems as incompleteness, ambiguities, and inconsistencies, which normally are discovered only in later stages of the design, can be detected in advance, as described by \cite{Trindade}. 
%Model checking algorithms can then verify the system model by systematically exploring all its states to check whether the requirements are met by the given system.
%
%Formal methods, alternatively, provide facilities for the modeling of each component of any complex system~\cite{Hall1990}. 
%
In this study, a mathematical model of each component of a stand-alone PV system, as panel solar, charge controller, batteries, inverter, and electrical load is created. The behavior of each system component can be analyzed and observed with the support of those formal models, as a joint operation of the components, which in this case represents the operation of the solar PV system itself. The project requirements, as battery autonomy and power demand, besides weather conditions, as solar irradiance and ambient temperature, are translated as part of the computer program and automatically verified during the formal process. The model checking tool reports in which conditions a system does not meet the user requirements. A key benefit to this approach is that it helps in the detection of flaws in the design phase of system development, thereby considerably improving system reliability~\cite{Akram2018}. 
%Those programs are viewed as mathematical objects, and the use of 
%Bringing this technique to solar PV systems, i
%Instead of finding a bug or a software inconsistence, t
%Here it will be verified a stand-alone PV system, with all their components modeled mathematically,   
%Among the non-deterministic variables considerated, is it worth to mention environmental issues (like solar irradiance, and temperature), and the variation of the electrical load (power consumption) or the battery' state of charge, as shown in Fig.\ref{fig:flowchartgeneral}.
The implementation of the proposed tool is carried out by means of the efficient SMT-based bounded model checker (ESBMC)~\cite{esbmc2018}. %, which allows one to incrementally verify a PV system as an imperative program using a fragment of decidable first-order theories~\cite{DBLP:books/daglib/0019162}.

@@

%The experimental results show that the proposed framework is more efficient \textcolor{red}{than what?} in different case studies to find not proper functioning of PV systems than simulation with off-the-shelf tool. 
%This is the first study to apply a formal verification technique to formally check the design of a stand-alone solar PV system. In summary, t
This paper makes two original contributions. % Firstly, we describe a modular modeling of each component of a PV system by means of mathematical models that can be encoded into fragments of first-order theories supported by software model checkers. Secondly
Firstly, we propose an automated verification method that formally checks the design of a given PV system using incremental model checking based on Satisfiability Module Theories (SMT), and that was never did before. Secondly, experimental results show that this proposed approach can find subtle design errors in PV systems, which are not easily detected by other approaches based on simulation.

@@

\textit{Outline}. Section~\ref{sec:SolarPhotovoltaicSystem} gives the background about solar PV systems, design and validation of PV systems, and the mathematical modeling. Section~\ref{sec:AutomatedVerification} presents the automated verification technique. The methodology is presented in section~\ref{sec:Methodology}. Section~\ref{sec:results} is devoted to the results. Section~\ref{sec:Conclusions} presents the conclusion and describes future work.

@@

\noindent where $ V_{in} $ is the voltage across the PV array, $ I_{in} $ is the output current of PV array, $ V_{out}=V_{b}=V_{system} $ is the  DC bus voltage, and $ I_{out} $ is the output current from the converter.

@@

%Therefore, with this equation it is possible to simulate the output power of the inverter, based on information from the inverter's data-sheet and from the DC module or the PV panel that feed the inverter (which are obtained by this study model). 
%
%
%--------------------------------------------------
\section{Verification of the PV Project Sizing}
%--------------------------------------------------
In addition to the verification tool being able to check a PV solar system, as if it were actually being used in the field, indicating the conditions that it does not meet the system user requirements, it is possible to extend the tool, giving it the capacity to carry out the validation of the designed system (a.k.a. sizing check).
%In addition the fact that the automated verification tool can check the possible failure of the PV system during its use at the field, it is possible as well to use the tool to check if the sizing of the components are correct.

Therefore this is a additional feature included at this paper. The sizing check will be performed, as proposed at the methodology, and the tool will indicate if there is an error of sizing before to perform the automated verification of the system. This stage ensures that the system meets the standard project steps related to the critical design month~\cite{Pinho}.
%
Firstly, it is needed to correct the energy consumption estimated to the load ($E_{consumption}$), which is carried out by ~\eqref{eq:Ecorrected}, where the efficiency of batteries ($\eta_{b}$), controller ($\eta_{c}$), and the inverter ($\eta_{i}$) are considered~\cite{Pinho}.
\begin{equation}
\label{eq:Ecorrected}
E_{corrected} = \dfrac{E_{consumption}}{ \eta_{b} \eta_{c} \eta_{i} }.
\end{equation}

@@

Particularly, the total number of panels in series ($N_{PSmin}$) and parallel ($N_{PPmin}$) are given by~\eqref{eq:NPSmin} and \eqref{eq:NPPmin}, respectively. With the check performed by (\ref{eq:NPS}) and (\ref{eq:NPP}), $ V_{system} $ is the DC voltage of the bus, normally $12$, $24$ or $48$ V.
\begin{equation}
\label{eq:NPSmin}
N_{PSmin} = \dfrac{V_{system}}{V_{m,ref}}.
\end{equation}

\begin{equation}
\label{eq:NPPmin}
N_{PPmin} = \dfrac{N_{TPmin}}{N_{PSmin}}.
\end{equation}

@@

Related to the batteries, firstly must be defined the total capacity of the battery bank, as described by \eqref{eq:Cbank} as
\begin{equation}
\label{eq:Cbank}
C_{bank} = \dfrac{E_{corrected} \times autonomy}{V_{system} \times DOD}.
\end{equation}
%
\noindent where the variable $autonomy$ is a design definition; % and normally has a value ranging from $6$ to $48$h; 
the other variables were discussed previously in Section~\ref{sec:PVmodel} and ~\ref{sec:BATmodel}.
%
Secondly, the total (minimum) number of batteries is computed, as described by \eqref{eq:Nbtotal}. Additionally, \eqref{eq:batcheck} performs the final sizing check, thus considering the number of batteries in series ($ N_{BS} $) and the number of batteries in parallel ($ N_{BP} $) that are established to the project.
\begin{equation}
\label{eq:Nbtotal}
N_{B}total = N_{BS}min \times N_{BP}min = \dfrac{V_{system}}{V_{bat}} \times \dfrac{C_{bank}}{C_{20}}.
\end{equation}

@@

Related to the charge controller, initially it must meet the voltage requirement of the PV system, as described by ~\eqref{eq:vcvsystem}: 
\begin{equation}
\label{eq:vcvsystem}
V_{c} = V_{system}.
\end{equation}

Following, the short circuit reference information from the manufacturer's solar panel must be corrected to the cell temperature, as described by \eqref{eq:iscamb}:
%
\begin{equation}
\label{eq:iscamb}
I_{sc,amb} = I_{sc,ref} \times \left[ 1 + \eta_{I} \times (T-25) \right]. 
\end{equation}

@@

The sizing project check of the inverter is carried out by means of three equations. Equation~\eqref{eq:vindc} ensures that the input voltage of the controller meets the system voltage. Equation~\eqref{eq:voutac} ensures that the output voltage of the controller meets the AC voltage of the load. Finally, \eqref{eq:invcheck} ensures that the controller can support the total demand of the load and the surge power.
%
\begin{equation}
\label{eq:vindc} 
V_{in}DC = V_{system}.
\end{equation}
%
\begin{equation}
\label{eq:voutac} 
V_{out}AC = V_{AC}.
\end{equation}
%
\begin{equation}
\label{eq:invcheck} 
\left[ (Demand \leq P_{AC,ref}) \, and \, (P_{surge} \leq MAX_{AC,ref}) \right].
\end{equation}

Worth to mention that the charge controller, the battery, and the inverter have a nominal efficiency presented at data sheets, and those numbers are very close to 100\%. However, based on empirical data, those efficiencies must be corrected, according to the loading of each component. If field or essay data is not available, considering that the proposed tools is aimed to be used prior the deployment of the PV system at the field, it is recommended (at least) to correct the battery efficiency ($\eta_{b}$) to 85\%.
%
%--------------------------------------------------
\section{Automated Verification Using Model Checking}
\label{sec:AutomatedVerification}
%--------------------------------------------------
%It is necessary to keep in mind that 
Validation is the process of determining whether a design meets the user requirements, whereas verification is the process of determining whether a design meets a set of requirements, specifications, and regulations~\cite{ClarkeHV18}. If the requirements, specifications, and regulations are given in a formal language, then it may be possible to automate the verification process, thus resulting in a process known as \textit{formal verification}. Verification may form part of a validation process.
%, but in general, validation cannot be formalized because it relates a system design to intent.  
While simulation and testing explore some of the possible behaviors and scenarios of the system, leaving open the question of whether the unexplored trajectories may contain a flaw, formal verification conducts an exhaustive exploration of all possible behaviors. Thus, when a design is pronounced correct by a formal verification method, it implies that all behaviors have been explored, and the questions of adequate coverage or a missed behavior becomes irrelevant \cite{Clarke2012}.
%Simulation may also be used for validation, but it is more problematic for verification.
%In order to use simulation for verification, it is necessary to ensure adequate coverage of operating conditions, scenarios, and system inputs. Testing can also be used for validation, however it is not feasible to cover all the aspects of the design space, and some times the real system must be used instead of a computing model.
 %

Formal verification is a systematic approach that applies mathematical reasoning to obtain guarantees about the correctness of a system; one successful method in this domain is model checking \cite{Clarke2012}.
%%%%%%%%Formal verification is a systematic approach that applies mathematical reasoning to obtain guarantees about the correctness of a system \cite{Forejt2011}; one successful method in this domain is model checking \cite{Clarke2012}.

% 
%Model checking is an automatic verification technique, as defined by \cite{ClarkeHV18}. Model checking was originally developed reasoned about finite state of concurrent systems, nowadays is mainly used to hardware and software verification, but can be applied to any kind of system. 
%
The process of model checking can be split into three main components: modeling, specification, and verification method. In modeling, a model (normally mathematical) of the system is created; in specification, normally a list of properties to be satisfied by the system is established, i.e., the requirements, normally  expressed in a temporal logic form as Computational Tree Logic (CTL) or Linear Temporal Logic (LTL).
%
%\begin{itemize}
%\item In modeling, a model (normally mathematical) of the system is created; 
%\item In specification, normally a list of properties to be satisfied by the system is established, i.e., the requirements, as reliability to performance for example. \item Normally is expressed in temporal logic form ($CTL$); 
%\item The model checking is the verification method itself. 
%\end{itemize}
%
The model checking algorithm can be described as \cite{ClarkeHV18}:  
%
\begin{itemize}
\item Given the model $M$ and a CTL (or LTL) formula $ \phi $ as input;  
\item Model checking algorithm provides all the states of model $ M $ which satisfies $ \phi $;  
\item It returns \textit{YES} if $ \phi $ is \textit{TRUE}, or returns \textit{NO} if $ \phi $ is \textit{FALSE}.  
\end{itemize}
Specifically for the \textit{FALSE} verification result, the algorithm returns a \textit{counterexample} (i.e., a sequence of states that leads to a property violation), which is useful as diagnostic of the system to discover in which situation the model is violated; this is the most important advantage of the use of model checking~\cite{ClarkeHV18}. 
%Among the other advantages can be listed: there is no need of proofs (the algorithm is not a deductive procedure), there is no problem with partial specifications of the system, logics can easily express many concurrency properties, is fast (compared to other rigorous methods such as interactive theorem proving). 
%
%The model checking problem can be defined as \cite{ClarkeHV18}: 
%
%\begin{itemize}
%\item Let $M$ be a Kripke structure (i.e., state transition graph);
%\item $f$ be the specification in temporal logic (a formula);
%\item Find all states $s$ of $M$ such that $M , s \models f$
%\end{itemize}
%
%Fig. \ref{fig:modelcheckstruc} shows the structure of a 
%In a typical model checking system, a preprocessor extracts a state transition graph from a system (program or circuit).
%
%\begin{figure}[h]
%\includegraphics[width=0.4\textwidth]{modelcheckstruc}
%\centering
%\caption{Model Checker structure (Source: \cite{ClarkeHV18})}
%\label{fig:modelcheckstruc}
%\end{figure}
%
%Here it is worth to mention that the term "model" is not the meaning taken from the dictionary. The problem is not dealing with an abstraction of the actual system under study. 
%
Fig.~\ref{fig:systemverif} shows a real PV system, and Fig.~\ref{fig:systemverif2} the conversion the system to be verified by a model checking procedure. % \textcolor{red}{Please try to adapt this figure to our context. How can it be applied to verify PV?}. 
%Fig.~\ref{fig:systemverif} shows the process to convert a real PV system to a model to be verified by a model checking procedure. % \textcolor{red}{Please try to adapt this figure to our context. How can it be applied to verify PV?}.

\begin{figure}[h]
\includegraphics[width=0.80\textwidth]{system_original_blocks}
\centering
\caption{Real system verification (adapted from \cite{ClarkeHV18}).}
\label{fig:systemverif}
\end{figure}

\begin{figure}[h]
\includegraphics[width=0.75\textwidth]{system_model_blocks}
\centering
\caption{Model checking verification \cite{ClarkeHV18}.}
\label{fig:systemverif2}
\end{figure}

However, there is a main disadvantage of model checking: the state explosion problem. In order to tackle this problem, many different techniques were developed in the last decades. One of the first major advances was symbolic model checking with binary decision diagrams (BDDs). In this approach, a set of states is represented by a BDD instead of by listing each state individually, which is often exponentially smaller in practice.
% Another major advance is the partial order reduction, which exploits the independence of actions in a system with asynchronous composition of processes \textcolor{red}{add citation here}. A third major advance is counterexample-guided abstraction refinement, which adaptively tries to find an appropriate level of refinement, not burdened with irrelevant detail that slows down verification \cite{Clarke2012}. 
%
Another promising approach to overcome state explosion problem is Bounded Model Checking (BMC)~\cite{DBLP:conf/tacas/BiereCCZ99}. BMC is a method that checks a model up to a given path in the path length. BMC algorithms traverse a finite state machine for a fixed number of steps, $ k $, and checks whether a property violation occurs with this bound. It uses Boolean Satisfiability (SAT) or Satisfiability Module Theories (SMT) solvers to check the generated formula from BMC.

>>>>

\begin{abstract}
With declining costs and increasing performance, the deployment of renewable energy systems is growing faster. In 2017, for the first time, the number of people without access to electricity dipped below 1 billion, but trends on energy access likewise fall short of global goals. Particular attention is given to stand-alone solar photovoltaic systems in rural areas or where grid extension is unfeasible. Tools to evaluate electrification projects are available, but they are based on simulations that do not cover all aspects of the design space. Automated verification using model checking has proven to be an effective technique to any kind of program verification. This paper marks the first application of software model checking to formally verify the design of a stand-alone solar photovoltaic system including solar panel, charge controller, battery, inverter, and electric load. Case studies, from real photovoltaic systems deployed in five different sites, ranging from 700W to 1,200W, were used to evaluate this proposed approach and to compare that with specialized simulation tools. Different verification tools were evaluated as well, in order to compare performance and soundness. Data from practical applications show the effectiveness of our approach, where specific conditions that lead to failures in a photovoltaic solar system are only detailed by the automated verification method.
\end{abstract}

@@

\section{Introduction}
Lack of access to clean and affordable energy is considered a core dimension of poverty~\cite{Hussein2012}. Progress has been made worldwide; in particular, the number of people without electricity access fell below 1 billion threshold for the first time in 2017~\cite{IEAweo2018}. The share of people without access to electricity from Africa is 58\%, while 19\% of the share comes from developing Asia, and 31\% from Latin America~\cite{IEAweo2018}. Numbers from Brazil show the aim to electrify 270 isolated places and 2.7 million of people until 2023~\cite{EPE2018}. Furthermore, there is a close relationship between the lack of energy and the low HDI (Human Development Index) of those localities~\cite{Coelho}.

@@

Formal methods based on model checking offer a great potential to obtain a more effective and faster verification in the design process~\cite{ClarkeHV18}.  
%with behavior that is, in principle, well determined. 
Any kind of system can be specified as computer programs using mathematical logic, which constitutes the intended (correct) behavior; then, one can try to give a formal proof or otherwise establish that the program meets its specification. %User or project requirements can be added during the creation of the formal model to be verified. %, as defined by \cite{Trindade}. 
%
%This area of research is referred as formal methods. % as defined in \cite{Clarkeetal}.
% Their aim is to establish system correctness with mathematical rigor. 
%In the recent decades, research in formal methods has led to the development of very promising verification techniques.
% that facilitate the early detection of bugs in order to ensure the correctness of the system. 
%
%Model-based verification techniques are based on models that describe the possible system behavior in a mathematically precise and unambiguous manner. 
%Thus, such problems as incompleteness, ambiguities, and inconsistencies, which normally are discovered only in later stages of the design, can be detected in advance, as described by \cite{Trindade}. 
%Model checking algorithms can then verify the system model by systematically exploring all its states to check whether the requirements are met by the given system.
%
%Formal methods, alternatively, provide facilities for the modeling of each component of any complex system~\cite{Hall1990}. 
%
In this study, a mathematical model of each component of a stand-alone PV system, as panel solar, charge controller, batteries, inverter, and electrical load is created. The behavior of each system component can be analyzed and observed with the support of those formal models, as a joint operation of the components, which in this case represents the operation of the solar PV system itself. The project requirements, as battery autonomy and power demand, besides weather conditions, as solar irradiance and ambient temperature, are translated as part of the computer program and automatically verified during the formal process. The model checking tool reports in which conditions a system does not meet the user requirements. A key benefit to this approach is that it helps in the detection of flaws in the design phase of system development, thereby considerably improving system reliability~\cite{Akram2018}. 
%Those programs are viewed as mathematical objects, and the use of 
%Bringing this technique to solar PV systems, i
%Instead of finding a bug or a software inconsistence, t
%Here it will be verified a stand-alone PV system, with all their components modeled mathematically,   
%Among the non-deterministic variables considerated, is it worth to mention environmental issues (like solar irradiance, and temperature), and the variation of the electrical load (power consumption) or the battery' state of charge, as shown in Fig.\ref{fig:flowchartgeneral}.
The implementation of the proposed tool is carried out by means of an algorithm written in language C, that is executed by three state-of-the-art model checkers to formally verifying PV designs, in order to evaluate performance and correctness: the C Bounded Model Checker (CBMC)~\cite{Kroening}, the Efficient SMT-based Bounded Model Checker (ESBMC)~\cite{esbmc2018}, and the Configurable Program Analysis Checker (CPAchecker).
%three the efficient SMT-based bounded model checker (ESBMC)~\cite{esbmc2018}. %, which allows one to incrementally verify a PV system as an imperative program using a fragment of decidable first-order theories~\cite{DBLP:books/daglib/0019162}.

@@

%The experimental results show that the proposed framework is more efficient \textcolor{red}{than what?} in different case studies to find not proper functioning of PV systems than simulation with off-the-shelf tool. 
%This is the first study to apply a formal verification technique to formally check the design of a stand-alone solar PV system. In summary, t
This paper makes three original contributions. % Firstly, we describe a modular modeling of each component of a PV system by means of mathematical models that can be encoded into fragments of first-order theories supported by software model checkers. Secondly
Firstly, we propose an algorithm written in language C that implements the automated verification method which formally checks the sizing and the operation of a given stand-alone PV system. Secondly, we evaluate the verification method by comparing three state-of-the-art model checkers in five real case studies. Thirdly, experimental results show that this proposed approach can find subtle design errors in stand-alone PV systems, which are not easily detected by other approaches based on simulation.

@@

\textit{Outline}. Section~\ref{sec:SolarPhotovoltaicSystem} gives the background about solar PV systems, design and validation of PV systems, and the mathematical modeling. Section~\ref{sec:AutomatedVerification} presents the automated verification technique. Section~\ref{sec:sizingcheck} shows how to perform the sizing of a stand-alone PV system. The methodology is presented in section~\ref{sec:Methodology}. Section~\ref{sec:results} is devoted to the results. Section~\ref{sec:Conclusions} presents the conclusion and describes future work.

@@

\noindent where $ V_{in} $ is the voltage across the PV array, $ I_{in} $ is the output current of PV array, $ V_{out} $ is the  DC bus voltage, and $ I_{out} $ is the output current from the converter.

@@

%Therefore, with this equation it is possible to simulate the output power of the inverter, based on information from the inverter's data-sheet and from the DC module or the PV panel that feed the inverter (which are obtained by this study model). 
%
%
%--------------------------------------------------
\subsection{Availability of Stand-alone PV Systems}
%--------------------------------------------------
Each stand-alone PV system, like any other power systems, has a specific level of availability. This reliability level impacts various issues, as system performance, production, feasibility, and investment. The availability of a stand-alone PV system can be defined as the percentage of time at which a power system is capable of meeting the load requirements~\cite{Khatib2014}. The number of hours that the system is available, divided by 8,760 h, gives the annual system availability.

The system availability definition depends on how critical the load application is. For critical loads, 99\% is considered acceptable. While in a ordinary house electrical load, 95\% is considered acceptable. As an example, a system with 95\% availability is expected to meet the load requirement of 8,322 h during an average year for the entire useful life of the system. An annual availability of 99\% means that the system can operate the load for 8,672 h of the 8,760 h.

With that in mind, it is important to mention that even if a formal verification or a simulation shows that a PV system fails, it doesn't mean that the sizing is wrong. It is important to evaluate how critical the load application is and the horizon of evaluation. However this analysis can be useful, for example, to improve the sized battery autonomy.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Automated Verification Using Model Checking}
\label{sec:AutomatedVerification}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Although simulation and testing explore possible behaviors and scenarios of a given system, they leave open the question of whether unexplored trajectories may contain a flaw. Formal verification conducts an exhaustive exploration of all possible behaviors; when a design is said to be ``correct'' by a formal verification method, it implies that all behaviors have been explored, and questions regarding adequate coverage or missed behavior becomes irrelevant~\cite{Clarke2012}. Formal verification is a systematic approach that applies mathematical reasoning to obtain guarantees about the correctness of a system; one successful method in this domain is model checking~\cite{Clarke2012}. Here we evaluate three state-of-the-art model checkers to formally verifying PV designs w.r.t. user requirements.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{CBMC}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

The C Bounded Model Checker (CBMC) falsifies assertions in C programs or proves that they are safe if a completeness threshold is given~\cite{Kroening}. CBMC implements a bit-precise translation of a C program, annotated with assertions and with loops unrolled up to a given depth, into a logical formula. If the formula is satisfiable, then a failing execution that leads to a violated assertion exists~\cite{Kroening}. CBMC's verification flow can be summarized in three stages: (i) Front-end: scans, parses and type-checks C code; it converts control flow elements, such as \textit{if} or \textit{switch} statements, loops and jumps, into equivalent guarded \textit{goto} statements, thus aiming to reduce verification effort; (ii) Middle-end: performs symbolic execution by eagerly unwinding loops up to a fixed bound, which can be specified by the user on a per-loop basis or globally, for all loops and finally; (iv) Back-end: supports SAT and SMT solvers to discharge verification conditions.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{ESBMC}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

ESBMC (or Efficient SMT-based Bounded Model Checker) is a bounded and unbounded mdoel checker for C programs~\cite{esbmc2018}, which supports the verification of LTL properties with bounded traces~\cite{DBLP:journals/sosym/MorseCN015}. ESBMC's verification flow can be summarized in three stages: (i) a front-end that can read and compile C code, where the system formal specification is first handled; (ii) preprocessing steps to deal with code representation, control flow and unwinding of loops, and model simplification, thereby aiming to reduce verification effort; and finally (iii) the SMT solving stage, where all constraints and properties of the system are encoded into SMT and checked for satisfiability. ESBMC exploits the standardized input language of SMT solvers (SMT-LIB\footnote{http://smtlib.cs.uiowa.edu/} logic format) to make use of a resource called \textit{assertion stack}~\cite{Morse2015}. This enables ESBMC, and the respective solver, to learn from previous checks, thus optimizing the search procedure and potentially eliminating a large amount of formula state space to be searched, because it solves and disregards data during the process, incrementally. This technique is called ``incremental SMT''~\cite{DBLP:journals/fac/SchrammelKBMTB17} and allows ESBMC to reduce the memory overhead, mainly when the verified system is complex and the computing platform does not have large amount of memory to deal with the entire design space state.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{CPAchecker}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Configurable program analysis (CPA) provides a conceptual basis for expressing different verification approaches in the same formal setting. The CPA formalism provides an interface for the definition of program analyses; consequently, the tool CPAchecker provides an implementation framework that allows the seamless integration of program analyses that are expressed in the CPA framework. The comparison of different approaches in the same experimental setting is intended to be easy and the experimental results is expected to be more meaningful~\cite{Beyer2011}. Related to the architecture, the central data structure is a set of control-flow automata (CFA), which consist of control-flow locations and control-flow edges. The CPA framework provides interfaces to SMT solvers and interpolation procedures, such that the CPA operators can be written in a concise and convenient way~\cite{Beyer2011}. Currently CPachecker uses MathSAT as an SMT solver, and CSIsat and MathSAT as interpolation procedures~\cite{Beyer2011}. The CPA algorithm performs the reachability analysis, and operates on an object of the abstract data type CPA, i.e., the algorithm applies operations from the CPA interface without knowing which concrete CPA it is analyzing. For most configurations, the concrete CPA will be a composite CPA, which implements the combination of different CPAs. In software verification, its usual to take a considerable amount of effort to convert a verification idea into actual experimental results — and CPAchecker aim to accelerate this process~\cite{Beyer2011}.
%
%--------------------------------------------------
\section{Stand-alone PV System Sizing and Verification}
\label{sec:sizingcheck}
%--------------------------------------------------
In addition to the verification tool being able to check a PV solar system, as if it were actually being used in the field, indicating the conditions that it does not meet the system user requirements, it is possible to extend the tool, giving it the capacity to carry out the validation of the designed system (a.k.a. sizing check).
%In addition the fact that the automated verification tool can check the possible failure of the PV system during its use at the field, it is possible as well to use the tool to check if the sizing of the components are correct.

Therefore this is a additional feature included at this paper. The sizing check will be performed by the proposed tool, and it will indicate if there is an error of sizing before to perform the automated verification of the system. This stage ensures that the system meets the standard project steps related to worst monthly average solar energy~\cite{Pinho}. 
%
Firstly, it is needed to correct the energy consumption estimated to the load ($E_{consumption}$), which is carried out by ~\eqref{eq:Ecorrected}, where the efficiency of batteries ($\eta_{b}$), controller ($\eta_{c}$), and the inverter ($\eta_{i}$) are considered~\cite{Pinho}.
\begin{equation}
\label{eq:Ecorrected}
E_{corrected} = \dfrac{E_{consumption}}{ \eta_{b} \eta_{c} \eta_{i} }.
\end{equation}

Following, it is necessary to estimate the energy that can be produced for each panel, called $E_{p}$, in Wh, as defined by~\eqref{eq:Ep}.

\begin{equation}
\label{eq:Ep}
E_{p} = Solar\_Irradiance \times Panel\_Area \times \eta_{p} \times 1000,
\end{equation}

\noindent where the solar irradiance is expressed in terms of $kWh/m^{2}$ and depends on the site where the PV systems will be deployed, the PV panel area is given in $m^{2}$ and corresponds to the size of one PV panel, and $\eta_{p}$ represents the PV panel efficiency.

@@

Particularly, the total number of panels in series ($N_{PSmin}$) and parallel ($N_{PPmin}$) are given by~\eqref{eq:NPSmin} and \eqref{eq:NPPmin}, respectively. With the check performed by (\ref{eq:NPS}) and (\ref{eq:NPP}). Where $V_{mppt,max}$ is the maximum operation voltage and $V_{mppt,min}$ is the minimum operation voltage of the charge controller; $V_{maxPower,TempMax}$ and $V_{maxPower,TempMin}$ are the maximum power voltage from the PV module considering the maximum and minimum operational temperature, respectively; $P_{total}$ is the total power demanded from the PV system and $P_{max,ref}$ is the power supplied from one PV panel in $Watts$.
%, $ V_{system} $ is the DC voltage of the bus, normally $12$, $24$ or $48$ V.

\begin{equation}
\label{eq:NPSmin}
\dfrac{V_{mppt,min}}{V_{maxPower,TempMax}}\leq N_{PSmin} \leq \dfrac{V_{mppt,max}}{V_{maxPower,TempMin}}.
\end{equation}

\begin{equation}
\label{eq:NPPmin}
N_{PPmin} = \dfrac{P_{total}}{Number\,Panels\,Series \times P_{max,ref}}.
\end{equation}

@@

Related to the batteries, firstly must be defined the total capacity of the battery bank, as described by \eqref{eq:Cbank} as
\begin{equation}
\label{eq:Cbank}
C_{bank} = \dfrac{E_{corrected} \times autonomy}{V_{system} \times DOD}.
\end{equation}
%
\noindent where the variable $autonomy$ is a design definition; % and normally has a value ranging from $6$ to $48$h; 
$ V_{system} $ is the DC voltage of the bus, and the other variables were discussed previously in Section~\ref{sec:PVmodel} and ~\ref{sec:BATmodel}.
%
Secondly, the total (minimum) number of batteries is computed, as described by \eqref{eq:Nbtotal}. Additionally, \eqref{eq:batcheck} performs the final sizing check, thus considering the number of batteries in series ($ N_{BS} $) and the number of batteries in parallel ($ N_{BP} $) that are established to the project.
\begin{equation}
\label{eq:Nbtotal}
N_{B}total = N_{BS}min \times N_{BP}min = \dfrac{V_{system}}{V_{bat}} \times \dfrac{C_{bank}}{1 \,Battery \, Capacity}.
\end{equation}

@@

Related to the charge controller, initially it must meet the voltage requirement of the PV system, as described by ~\eqref{eq:vcvsystem} to the charge controller voltage: 
\begin{equation}
\label{eq:vcvsystem}
V_{c} = V_{system}.
\end{equation}

Following, the short circuit reference information from the manufacturer's solar panel must be corrected to the cell temperature, as described by \eqref{eq:iscamb}:
%
\begin{equation}
\label{eq:iscamb}
I_{sc,amb} = \dfrac{G}{G_{ref}} \left[ I_{sc,ref} + \mu_{I} \times (T-25) \right]. 
\end{equation}

@@

The sizing project check of the inverter is carried out by means of three equations. Equation~\eqref{eq:vindc} ensures that the input voltage of the controller meets the system voltage. Equation~\eqref{eq:voutac} ensures that the output voltage of the controller meets the AC voltage of the load. Finally, \eqref{eq:invcheck} ensures that the controller can support the total demand of the load and the surge power. Where $V_{in}DC$ is the nominal input voltage and $V_{out}AC$ is the nominal output voltage of the inverter; $MAX_{AC,ref}$ is the peak power that the inverter can support.
%
\begin{equation}
\label{eq:vindc} 
V_{in}DC = V_{system}.
\end{equation}
%
\begin{equation}
\label{eq:voutac} 
V_{out}AC = V_{AC}.
\end{equation}
%
\begin{equation}
\label{eq:invcheck} 
\left[ (Demand \leq P_{AC,ref}) \, and \, (P_{surge} \leq MAX_{AC,ref}) \right].
\end{equation}

Worth to mention that the charge controller, the battery, and the inverter have a nominal efficiency presented at data sheets, and those numbers are very close to 100\%. However, based on empirical data, those efficiencies must be corrected, according to the loading of each component. If field or essay data is not available, considering that the proposed tools is aimed to be used prior the deployment of the PV system at the field, it is recommended (at least) to correct the battery efficiency ($\eta_{b}$) to 85\%, keeping the remaining efficiencies as expressed by the manufacturers.
%
%----------------------------------------
\section{Proposed Automated Verification Method of PV Systems}
\label{sec:Methodology}
%----------------------------------------
%
%Fig. \ref{fig:statetransition} shows the state diagram for the proposed tool. 
%
%\begin{figure}[h]
%\includegraphics[width=0.5\textwidth]{statetransition}
%\centering
%\caption{State transition diagram to the proposed automated verification.}
%\label{fig:statetransition}
%\end{figure}
%
%It is worth mentioning that the steps described here are carried out shortly after the design of the solar photovoltaic system, as soon as the equipment and equipment specifications are defined; before buying and deploying them, as a way to ensure that the project will not fail. 
%
The flowchart of the proposed automated verification method is illustrated in Fig.~\ref{fig:flowchartgeneral}.
